% Overleaf: main.tex | pdfLaTeX
% ATS-friendly: plain text, standard sections, clear headings
\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.4cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Clean sans — regular weight
\usepackage[scaled=0.95]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\cvsection}[1]{%
  \vspace{1.2em}%
  {\large\textbf{\MakeUppercase{#1}}}\\[0.2em]
  \hrule
  \vspace{0.6em}%
}
\newcommand{\jobentry}[4]{%
  \textbf{#1} \hfill {\small #2}\\
  \textit{#3} \hfill {\small #4}\\[0.2em]
}

\begin{document}

% ── Header ──
\begin{center}
  {\LARGE \textbf{Ece Dalpolat}}\\[0.4em]
  {\large AI Engineer \& Data Scientist}\\[0.4em]
  {\small
  +90 552 360 9850 \,|\, ecedlplt9850@gmail.com \,|\, Istanbul\\[0.2em]
  \href{https://ecedalpolat.github.io/ece-dalpolat-portfolio/}{Portfolio} \,|\,
  \href{https://github.com/EceDalpolat}{GitHub} \,|\,
  \href{https://www.linkedin.com/in/ece-dalpolat-0265a0221/}{LinkedIn}
  }
\end{center}

\vspace{-0.5em}
\cvsection{Profile}

AI Engineer and Data Scientist who builds production AI systems---not just demos. At Qkare, I own real systems used by corporate customers: the dbt data layer that feeds dashboards, LangChain/LangGraph agents that answer questions over psychometric data, and FastAPI services that recommend KPIs and job competencies with validated JSON output.

What I do day-to-day: model data in SQL (109+ dbt models, native PostgreSQL row-level security, Superset), design LLM pipelines (RAG, semantic cache, prompt-injection guards), ship microservices behind a shared agent gateway, and measure quality with LLM-as-judge evals before release. I take problems from messy requirements to Docker/Kubernetes deployment with CI, tenant isolation, and cost-aware inference.

% ── Experience ──
\cvsection{Experience}

\jobentry{AI Engineer}{Jun 2025 -- Present}{Qkare}{Istanbul}
\begin{itemize}[leftmargin=1.5em, nosep, topsep=2pt, itemsep=2pt]
  \item Lead: dbt layer, production AI agents/advisors, gateway, and security across 8+ shipped systems.
\end{itemize}
\vspace{0.6em}

\jobentry{Teaching Assistant}{Jan 2025 -- Present}{Miuul}{Remote}
\begin{itemize}[leftmargin=1.5em, nosep, topsep=2pt, itemsep=2pt]
  \item Data science and machine learning lectures; project mentoring and evaluation.
\end{itemize}
\vspace{0.6em}

\jobentry{Graduate Research Assistant}{Jan 2024 -- Jun 2025}{Işık University}{Istanbul}
\begin{itemize}[leftmargin=1.5em, nosep, topsep=2pt, itemsep=2pt]
  \item Software labs; supervised data science and deep learning projects.
\end{itemize}
\vspace{0.6em}

\jobentry{Research Data Scientist}{Jan 2024 -- Jun 2025}{Top4Honeychains}{}
\begin{itemize}[leftmargin=1.5em, nosep, topsep=2pt, itemsep=2pt]
  \item Honey value-chain ETL, TensorFlow/scikit-learn models, REST API integrations.
\end{itemize}

% ── Projects ──
\cvsection{Projects}

\textbf{Analytics Platform} \,|\, \textit{Qkare} \hfill Nov 2025 -- May 2026\\
End-to-end HR analytics: PostgreSQL FDW, 109 dbt models, 56 marts, 13 AI precompute tables, native RLS, Superset. Lead: dbt layer.
\vspace{0.5em}

\textbf{Analyzer Platform} \,|\, \textit{Qkare} \hfill Apr 2025 -- May 2026\\
LangChain ReAct agent on psychometric marts; 4-layer security, JWT+RLS, Langfuse. Lead: security and config bootstrap.
\vspace{0.5em}

\textbf{Coach Platform} \,|\, \textit{Qkare} \hfill Sep 2025 -- Nov 2025\\
Multi-agent coaching (LangGraph, POML, OpenAI Realtime). Referee Agent (LLM-as-judge), voice stack, eval tooling.
\vspace{0.5em}

\textbf{Skills Advisor} \,|\, \textit{Qkare} \hfill Aug 2025 -- May 2026\\
12 competency dimensions from closed dictionary; LangChain or DSPy ensemble. Primary engineer.
\vspace{0.5em}

\textbf{KPI Advisor} \,|\, \textit{Qkare} \hfill Apr 2026 -- May 2026\\
SMART KPIs via APQC PCF; lexical retrieval, Golden Dataset, LLM-as-judge pipeline. Primary engineer.
\vspace{0.5em}

\textbf{Agent API Gateway} \,|\, \textit{Qkare} \hfill Apr 2026 -- May 2026\\
FastAPI monorepo, unified invoke API, JWT, per-agent Docker/CI. Platform lead.
\vspace{0.5em}

\textbf{QKare AI Assistant} \,|\, \textit{Qkare} \hfill Jul 2025\\
Corporate chatbot: rule, semantic cache (FAISS/Milvus), RAG, LLM; hybrid security. Sole author.
\vspace{0.5em}

\textbf{Behavioral Clustering R\&D} \,|\, \textit{Qkare} \hfill Aug 2025\\
K-Means, DBSCAN, GMM; PCA/t-SNE; fed Analytics marts. Sole author.
\vspace{0.5em}

\textbf{CVAnalyzerAI} \hfill 2025\\
MCP resume analysis (FastAPI, DSPy, ANTLR). github.com/EceDalpolat/cvAnalizerAI
\vspace{0.5em}

\textbf{TOP4HONEYCHAINS} \hfill 2024--2025\\
Honey traceability ML, REST APIs, time-series forecasting.
\vspace{0.5em}

\textbf{Marketing Campaign Prediction}\\
Bank campaign model: SMOTE, XGBoost, Streamlit.
\vspace{0.5em}

\textbf{Pollen Classification}\\
CNN classifier, 90\%+ accuracy; data augmentation.
\vspace{0.5em}

\textbf{Antenna Behaviour Analysis}\\
DeepLabCut keypoint tracking; movement analysis.
\vspace{0.5em}

\textbf{Student Success Analysis}\\
Random Forest on academic features; Tkinter GUI.

% ── Skills ──
\cvsection{Skills}

\textbf{AI/LLM:} LangChain, LangGraph, DSPy, RAG, OpenAI API, Pydantic, LLM-as-judge\\[0.2em]
\textbf{Data:} dbt Core, PostgreSQL, Apache Superset, Pandas, SQL\\[0.2em]
\textbf{Backend:} FastAPI, httpx, WebSocket, JWT, MCP, REST\\[0.2em]
\textbf{Infra:} Docker, Kubernetes, GitLab CI/CD, Redis, OpenTelemetry, Langfuse\\[0.2em]
\textbf{Languages:} Python, SQL, JavaScript, Java, C\#

% ── Education ──
\cvsection{Education}

\textbf{MSc Information Technologies} \hfill 2022 -- Present\\
Işık University --- GPA 3.57. Thesis: ML in beekeeping and honey extraction.
\vspace{0.5em}

\textbf{BSc Software Engineering} \hfill 2018 -- 2023\\
Kırklareli University --- GPA 2.71

% ── Certificates ──
\cvsection{Certificates}

Miuul Data Scientist Bootcamp; Miuul Machine Learning; Miuul Generative AI; Udemy LangChain/RAG; BTK SQL; Huawei HCCDA-AI

\vspace{0.8em}
\begin{center}
  {\small Turkish (native) \,|\, English (B2)}
\end{center}

\end{document}
