% Overleaf: main.tex | pdfLaTeX
% ATS-friendly: plain text, standard sections, no tables/icons/bars
\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.6cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Clean sans — regular weight (not bold, not italic)
\usepackage[scaled=0.95]{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Section titles: normal weight (not bold) — only job/project names use \textbf
\newcommand{\cvsection}[1]{%
  \vspace{0.7em}%
  {\normalsize\fontseries{m}\selectfont #1}\\[0.25em]
}
\newcommand{\jobentry}[4]{%
  \textbf{#1} \hfill {\small #2}\\
  {\small #3} \hfill {\small #4}\\[0.2em]
}

\begin{document}

% ── Header ──
{\LARGE Ece Dalpolat} \hfill AI Engineer \& Data Scientist\\[0.35em]
{\small
+90 552 360 9850 \,|\, ecedlplt9850@gmail.com \,|\, Istanbul \,|\,
\href{https://ecedalpolat.github.io/ece-dalpolat-portfolio/}{Portfolio} \,|\,
\href{https://github.com/EceDalpolat}{GitHub} \,|\,
\href{https://www.linkedin.com/in/ece-dalpolat-0265a0221/}{LinkedIn}
}

\cvsection{Profile}

AI Engineer and Data Scientist who builds production AI for HR and talent analytics --- not demos. At Qkare I own real systems used by corporate customers: the dbt data layer that feeds dashboards, LangChain and LangGraph agents that answer questions over psychometric data, and FastAPI services that recommend KPIs and job competencies with validated JSON output.

What I do day to day: model data in SQL (109+ dbt models, native PostgreSQL row-level security, Superset), design LLM pipelines (RAG, semantic cache, prompt-injection guards), ship microservices behind a shared agent gateway, and measure quality with LLM-as-judge evals before release. I am comfortable taking a problem from messy requirements to Docker/Kubernetes deployment with CI, tenant isolation, and cost-aware inference.

MSc in Information Technologies (Işık University). I also teach data science and machine learning at Miuul. Open to AI engineering, data engineering, and ML platform roles where the work ships to production.

% ── Experience ──
\cvsection{Experience}

\jobentry{AI Engineer}{Jun 2025 -- Present}{Qkare}{Istanbul}
\begin{itemize}[leftmargin=1.2em, nosep, topsep=2pt]
  \item Lead: dbt layer, production AI agents/advisors, gateway, and security across 8+ shipped systems.
\end{itemize}

\jobentry{Teaching Assistant}{Jan 2025 -- Present}{Miuul}{Remote}
\begin{itemize}[leftmargin=1.2em, nosep, topsep=2pt]
  \item Data science and machine learning lectures; project mentoring and evaluation.
\end{itemize}

\jobentry{Graduate Research Assistant}{Jan 2024 -- Jun 2025}{Işık University}{Istanbul}
\begin{itemize}[leftmargin=1.2em, nosep, topsep=2pt]
  \item Software labs; supervised data science and deep learning projects.
\end{itemize}

\jobentry{Research Data Scientist}{Jan 2024 -- Jun 2025}{Top4Honeychains}{}
\begin{itemize}[leftmargin=1.2em, nosep, topsep=2pt]
  \item Honey value-chain ETL, TensorFlow/scikit-learn models, REST API integrations.
\end{itemize}

% ── Projects ──
\cvsection{Projects}

\textbf{Analytics Platform} \hfill Nov 2025 -- May 2026\\
Qkare --- End-to-end HR analytics: PostgreSQL FDW, 109 dbt models, 56 marts, 13 AI precompute tables, native RLS, Superset. Lead: dbt layer.

\vspace{0.25em}
\textbf{Analyzer Platform} \hfill Apr 2025 -- May 2026\\
Qkare --- LangChain ReAct agent on psychometric marts; 4-layer security, JWT+RLS, Langfuse. Lead: security and config bootstrap.

\vspace{0.25em}
\textbf{Coach Platform} \hfill Sep 2025 -- Nov 2025\\
Qkare --- Multi-agent coaching (LangGraph, POML, OpenAI Realtime). Referee Agent (LLM-as-judge), voice stack, eval tooling.

\vspace{0.25em}
\textbf{Skills Advisor} \hfill Aug 2025 -- May 2026\\
Qkare --- 12 competency dimensions from closed dictionary; LangChain or DSPy ensemble. Primary engineer.

\vspace{0.25em}
\textbf{KPI Advisor} \hfill Apr 2026 -- May 2026\\
Qkare --- SMART KPIs via APQC PCF; lexical retrieval, Golden Dataset, LLM-as-judge pipeline. Primary engineer.

\vspace{0.25em}
\textbf{Agent API Gateway} \hfill Apr 2026 -- May 2026\\
Qkare --- FastAPI monorepo, unified invoke API, JWT, per-agent Docker/CI. Platform lead.

\vspace{0.25em}
\textbf{QKare AI Assistant} \hfill Jul 2025\\
Qkare --- Corporate chatbot: rule, semantic cache (FAISS/Milvus), RAG, LLM; hybrid security. Sole author.

\vspace{0.25em}
\textbf{Behavioral Clustering R\&D} \hfill Aug 2025\\
Qkare --- K-Means, DBSCAN, GMM; PCA/t-SNE; fed Analytics marts. Sole author.

\vspace{0.25em}
\textbf{CVAnalyzerAI} \hfill 2025\\
MCP resume analysis (FastAPI, DSPy, ANTLR). github.com/EceDalpolat/cvAnalizerAI

\vspace{0.25em}
\textbf{TOP4HONEYCHAINS} \hfill 2024--2025\\
Honey traceability ML, REST APIs, time-series forecasting.

\vspace{0.25em}
\textbf{Marketing Campaign Prediction}\\
Bank campaign model: SMOTE, XGBoost, Streamlit.

\vspace{0.25em}
\textbf{Pollen Classification}\\
CNN classifier, 90\%+ accuracy; data augmentation.

\vspace{0.25em}
\textbf{Antenna Behaviour Analysis}\\
DeepLabCut keypoint tracking; movement analysis.

\vspace{0.25em}
\textbf{Student Success Analysis}\\
Random Forest on academic features; Tkinter GUI.

% ── Skills ──
\cvsection{Skills}

\textbf{AI/LLM:} LangChain, LangGraph, DSPy, RAG, OpenAI API, Pydantic, LLM-as-judge\\
\textbf{Data:} dbt Core, PostgreSQL, Apache Superset, Pandas, SQL\\
\textbf{Backend:} FastAPI, httpx, WebSocket, JWT, MCP, REST\\
\textbf{Infra:} Docker, Kubernetes, GitLab CI/CD, Redis, OpenTelemetry, Langfuse\\
\textbf{Languages:} Python, SQL, JavaScript, Java, C\#

% ── Education ──
\cvsection{Education}

\textbf{MSc Information Technologies} \hfill 2022 -- Present\\
Işık University --- GPA 3.57. Thesis: ML in beekeeping and honey extraction.

\vspace{0.25em}
\textbf{BSc Software Engineering} \hfill 2018 -- 2023\\
Kırklareli University --- GPA 2.71

% ── Certificates ──
\cvsection{Certificates}

Miuul Data Scientist Bootcamp; Miuul Machine Learning; Miuul Generative AI; Udemy LangChain/RAG; BTK SQL; Huawei HCCDA-AI

\vspace{0.3em}
{\small Turkish (native) | English (B2)}

\end{document}
